Fourmile

### 2022-08-02 fourmile_dataprocess.Rmd
monthly sum of loss for lower gages

DS1 minus US1 (uppermost)

@@

Average DS1 minus US1 difference

@@

USGS2 minus DS1

@@

Average USGS2 minus DS1 difference

@@

USGS1 minus USGS2

@@

ggplotly(diff3)
```

Average USGS1 minus USGS2 difference

```{r USGS1-USGS2_avg, echo=FALSE}
mean(diff_usgs1$q_m3s, na.rm=T)

@@

>>>>

### DS1 minus US1 (uppermost)

@@

#### Average DS1 minus US1 difference

@@

### USGS2 minus DS1

@@

#### Average USGS2 minus DS1 difference

@@

### USGS1 minus USGS2

@@

ggplotly(diff3)

#### Average USGS1 minus USGS2 difference

```{r USGS1-USGS2_avg, echo=FALSE}

mean(diff_usgs1$q_m3s, na.rm=T)

@@

#### Sum of losses between USGS1 and USGS2

```{r USGS1-USGS2 sum of losses, echo=FALSE}

sum_diff_usgs1 <- diff_usgs1 %>%
  mutate(month = as.numeric(format(date, "%m")), year = as.numeric(format(date, "%Y"))) %>%
  mutate(neg_q = if_else(q_m3s < 0, q_m3s, 0)) %>%
  dplyr::group_by(year, month) %>%
  dplyr::summarize(mo_loss = sum(q_m3s)) %>%
  #distinct() %>%
  na.omit()

kable(sum_diff_usgs1, 
      col.names = c("Year", "Month", "Monthly sum of losses (m3/s)")) %>%
  kable_styling()
